## rgbif use case No. 1 - Ecological niche modelling (aka species distribution modelling)

In this example, we plot actual occurrence data for *Bradypus* species against a single predictor variable, BIO1 (annual mean temperature). This is only ont step in a species distribution modelling nworkflow.

This example can be done using BISON data as well with our rbison package.

```{r defaults, eval=TRUE, echo=FALSE}
opts_chunk$set(comment=NA, warning=FALSE, message=FALSE, fig.width=7, fig.height=6)
```

### Load libraries

```{r load, comment=NA, cache=TRUE}
library(rgbif)
library(dismo)
library(maptools)
```

### Make a list of files that are installed with the dismo package, then create a rasterStack from these

```{r sdm1, cache=TRUE}
files <- list.files(paste(system.file(package="dismo"), '/ex', sep=''), 'grd', full.names=TRUE)
predictors <- stack(files)
```

### Get world boundaries.

```{r sdm2, cache=TRUE}
data(wrld_simpl)
```

### Get GBIF data using the rOpenSci package rgbif.

```{r sdm3, cache=TRUE}
df <- occurrencelist(scientificname='bradypus*', coordinatestatus=TRUE, maxresults=500)
df <- gbifdata(df, coordinatestatus=TRUE)
df2 <- data.frame(lon=df$decimalLongitude, lat=df$decimalLatitude)
```

### Plot: (1) Add raster data, (2) Add political boundaries, (3) Add the points (occurrences)

```{r sdm4, cache=TRUE}
plot(predictors, 1)
plot(wrld_simpl, add=TRUE)
points(df2, col='blue')
```

### Further reading

The above example comes from [this tutorial][sdm] on species distribution modeling. 

[sdm]: http://cran.r-project.org/web/packages/dismo/vignettes/sdm.pdf